Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-29 xrb2/paper.tex
add clarifying sentence for F500 phase plot

In both the $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} and the $u$-$v$ phase plot in Figure~\ref{fig:uv_hot}, the horizontal $u$-velocity for the $\tt{F500\_4e8}$ (right panel) burning region is slightly larger than that of the cooler runs. Additionally, the cooler runs' $u$-velocities are two to three orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. These phase plot velocities therefore most likely correspond to vortical motion in the turbulent burning vortices rather than the propagation of a flame itself. The vertical $z$-velocity $v$ in Figure~\ref{fig:uv_hot} further suggests that $\tt{F500\_4e8}$ undergoes increased vortical motion, as we see that the velocity magnitude in the burning region is significantly larger than in the lower temperature runs. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$). As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what we saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.

>>>>

In both the $u$-$\rho$ phase plot in Figure~\ref{fig:urho_hot} and the $u$-$v$ phase plot in Figure~\ref{fig:uv_hot}, the horizontal $u$-velocity for the $\tt{F500\_4e8}$ (right panel) burning region is slightly larger than that of the cooler runs. Additionally, the cooler runs' $u$-velocities are two to three orders of magnitude greater than the flame speeds listed in Table~\ref{table:flame_speeds}. These phase plot velocities therefore most likely correspond to vortical motion in the turbulent burning vortices rather than the propagation of a flame itself. The vertical $z$-velocity $v$ in Figure~\ref{fig:uv_hot} further suggests that $\tt{F500\_4e8}$ undergoes increased vortical motion, as we see that the velocity magnitude in the burning region is significantly larger than in the lower temperature runs.
Also of interest in these plots is that the coolest run shows high velocity material comprising both high and low $\dot{e}_{\rm nuc}$ with horizontal velocity asymmetry, both of which suggest the burning vortex in the coolest case is less well defined than at higher temperatures. The coolest run thus does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs at this time ($40~\mathrm{ms}$).
As can be seen in Figure~\ref{fig:uv} (which was plotted at $100~\mathrm{ms}$), this does develop more at later times. Similar to what we saw when comparing the runs with different rotation rates, it would therefore appear that it takes longer for the flame to develop when $T_{\rm star}$ is cooler.
